`r paste(params$species)` biomass trends and figures

### 2019-12-04 analysis/VOCC/3-bioclimatic-trends.Rmd
calculate bioclimatic estimates from series of separate models and prediction work-arounds

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

paste("region =", region)
paste("ssids modelled separately =", bind_predictions)
paste("model label =", covs)
paste("priors =", priors)

@@

if (any(names(maturity) == "adult_density")) {
#if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
  adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  #nd$year <- as.integer(nd$year)
  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(adult_biomass$data$year)) %>% 
    mutate(
      do_mlpl_scaled = (log_do - adult_biomass$data$do_mlpl_mean[1]) /(adult_biomass$data$do_mlpl_sd[1]*2), 
      do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)

@@

  adult_predictions$est_rw_i <- adult_predictions_obj$obj$report()$proj_rw_i
  # test_eta <- adult_predictions_obj$obj$report()$proj_eta
  # test_fe <- adult_predictions_obj$obj$report()$proj_fe
  # 
  # test_diff <- test_eta - test_fe
  # range(adult_predictions$est_rw_i)
  # report <- adult_predictions_obj$obj$report()

  saveRDS(adult_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-bioclimatic-prior-", priors, ".rds"))

  imm_biomass <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

    nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(imm_biomass$data$year))%>% 
    mutate(do_mlpl_scaled = (log_do - imm_biomass$data$do_mlpl_mean[1]) /(imm_biomass$data$do_mlpl_sd[1]*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)
  #nd$year <- as.numeric(nd$year)

@@

  imm_predictions$est_rw_i <- imm_predictions_obj$obj$report()$proj_rw_i

  saveRDS(imm_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-bioclimatic-prior-", priors, ".rds"))

} else {

    total_biomass <- readRDS(paste0("data/", spp, 
      "/model-total-biomass-", spp, "-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))

    nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
    nd <- nd_all %>% 
      filter(ssid %in% model_ssid) %>%
      filter(year %in% unique(total_biomass$data$year))%>% 
    mutate(do_mlpl_scaled = (log_do - total_biomass$data$do_mlpl_mean) /(total_biomass$data$do_mlpl_sd*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    predictions <- predict(total_biomass, newdata = nd)
    saveRDS(predictions, file = paste0("data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"))
}
```

@@

if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-mature-bioclimatic-prior-", priors, ".rds"
  )) %>% filter(ssid %in% model_ssid))
  try(imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-imm-bioclimatic-prior-", priors, ".rds"
  )) %>% filter(ssid %in% model_ssid))

@@

  try({adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-bioclimatic-prior-", priors, ".rds"
    ))
  })
  try({imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-bioclimatic-prior-", priors, ".rds"
    ))
  })

  # OR bind together predictions from different models
  if (bind_predictions) {
    try({pred1n3 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred4 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred16 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-16-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })

    if (!exists("pred1n3")) pred1n3 <- NULL
    if (!exists("pred16")) pred16 <- NULL
    if (!exists("pred4")) pred4 <- NULL
    adult_predictions <- rbind(pred1n3, pred4, pred16)

    try({pred1n3_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-imm-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred4_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-imm-bioclimatic-prior-", priors, ".rds"))
    })
    try({pred16_imm <- readRDS(paste0("data/", spp,
        "/predictions-", spp, covs, "-16-imm-bioclimatic-prior-", priors, ".rds"))
    })

    if (!exists("pred1n3_imm")) pred1n3_imm <- NULL
    if (!exists("pred16_imm")) pred16_imm <- NULL
    if (!exists("pred4_imm")) pred4_imm <- NULL
    imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm)
  }
  }

@@

      if (!exists("predictions")) {
        try({pred1n3_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-1n3-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({pred4_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-4-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({pred16_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-16-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({
          predictions <- rbind(pred1n3_all, pred4_all, pred16_all)
        })

@@

if (exists("adult_predictions")) {
  # to convert from kg/m2 to kg/hectare multiply by 10000
  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000
  adult_predictions$bioclimatic <- exp(adult_predictions$est - adult_predictions$epsilon_st) * 10000
  imm_predictions$bioclimatic <- exp(imm_predictions$est - imm_predictions$epsilon_st) * 10000

  adult_predictions$total_bio <- imm_predictions$est_exp + adult_predictions$est_exp
  imm_predictions$prop_imm <- 
  imm_predictions$est_exp / (adult_predictions$est_exp + imm_predictions$est_exp)

@@

  predictions$est_exp <- exp(predictions$est) * 10000
  predictions$bioclimatic <- exp(predictions$est - predictions$epsilon_st) * 10000

  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .999)
  #max_bio <- round(max(predictions$total_bio))
  max_bio <- signif(max(predictions$est_exp), digits = 2)

@@

Save trend plots
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/trends-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 11,
  height = 8.5
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

@@

png(
  file = paste0("figs/", spp, "/bioclimatic-biomass-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 16,
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = biomass_plots,
  nrow = 2
)
dev.off()
```

Save plot medley
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/bioclimatic-exploratory-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 9.5,
  height = 12.5
)

@@

png(
  file = paste0("figs/", spp, "/bioclimatic-residuals-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 16,
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = p_adult_st,
  nrow = 2
)
dev.off()
```

>>>>

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Pacific Cod" # 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-all" 
    # year_cutoff: 2012
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

paste("species =", species)
paste("region =", region)
paste("ssids modelled separately =", bind_predictions)
paste("model label =", covs)
paste("priors =", priors)

@@

if (any(names(maturity) == "adult_density")) {
#if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))

  adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "--", ssid_string, "-prior-", priors, ".rds"))
  #nd$year <- as.integer(nd$year)

  sort(unique(nd_all$year))
  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(adult_biomass$data$year)) %>% 
    mutate(
      do_mlpl_scaled = (log_do - adult_biomass$data$do_mlpl_mean[1]) /(adult_biomass$data$do_mlpl_sd[1]*2), 
      do_mlpl_scaled2 = do_mlpl_scaled^2) %>% 
    select(-est, -est_non_rf, - est_rf, -omega_s, -epsilon_st, -zeta_s)
  nd <- na.omit(nd)
  sort(unique(nd$year))

@@

  nd_pre_2013 <- nd %>% filter(year < 2013)
  ad_model_2013 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2013-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2013 <- predict(ad_model_2013, newdata = nd_pre_2013, return_tmb_object = TRUE)

  fake_2013 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) %>% filter(year < 2013 )
  sort(unique(fake_2013$year))
  sort(unique(nd_pre_2013$year))
  adult_2013 <- predict(ad_model_2013, newdata = fake_2013, return_tmb_object = TRUE)
  adult_2013$data$year <- adult_2013$data$year + 2

  nd_pre_2015 <- nd %>% filter(year < 2015)
  ad_model_2015 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2015-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2015 <- predict(ad_model_2015, newdata = nd_pre_2015, return_tmb_object = TRUE)

  fake_2015 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) %>% filter(year < 2015)
  sort(unique(nd_pre_2015$year))
  sort(unique(fake_2015$year))
  adult_2015 <- predict(ad_model_2015, newdata = fake_2015, return_tmb_object = TRUE)
  adult_2015$data$year <- adult_2015$data$year + 2

  nd_pre_2017 <- nd %>% filter(year < 2017)
  ad_model_2017 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2017-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2017 <- predict(ad_model_2017, newdata = nd_pre_2017, return_tmb_object = TRUE)

  fake_2017 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) #%>% filter(year < 2013 )
  sort(unique(fake_2017$year))
  sort(unique(nd_pre_2017$year))

  adult_2017 <- predict(ad_model_2017, newdata = fake_2017, return_tmb_object = TRUE)
  adult_2017$data$year <- adult_2017$data$year + 2

  fake_2017_minus4 <- nd %>% 
    mutate(year = year - 4) %>% 
    filter(year > 2007)
  sort(unique(fake_2017_minus4$year))
  adult_2017_multi <- predict(ad_model_past, newdata = fake_2017_minus4, return_tmb_object = TRUE)
  adult_2017_multi$data$year <- adult_2017_multi$data$year + 4
  sort(unique(adult_2017_multi$data$year))

 past_predictions <- adult_pre_2015$data %>% 
   mutate(past_est = est, blob_bioclim = est) %>% 
   select(X, Y, year, past_est, blob_bioclim)

   bioclim_2013_start <- filter(adult_pre_2013$data, year >= 2011) %>% filter(year <= 2012) %>%
    mutate(bioclim_2013 = est)
  bioclim_2013_end <- filter(adult_2013$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2013 = est_non_rf + omega_s)
  bioclim_2013 <- dplyr::bind_rows(bioclim_2013_start, bioclim_2013_end)

  bioclim_2015_start <- filter(adult_past$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2015 = est) %>% select(X,Y, year, bioclim_2015)
  bioclim_2013 <- left_join(bioclim_2013, bioclim_2015_start) %>% 
    select(X,Y, year, bioclim_2013, bioclim_2015)
  past_predictions <- left_join(past_predictions, bioclim_2013)

  bioclim_2015 <- filter(adult_2015$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(blob_bioclim = est_non_rf + omega_s, bioclim_2015 = est_non_rf + omega_s)

  bioclim_2017_start <- filter(adult_2017$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(bioclim_2017 = est) %>% select(X,Y, year, bioclim_2017)

  bioclim_2015 <- left_join(bioclim_2015, bioclim_2017_start)

  bioclim_2017_multi <- filter(adult_2017_multi$data, year >= 2017) %>% filter(year <= 2018) %>%
    mutate(blob_bioclim = est_non_rf + omega_s) %>% 
    select(X,Y, year, blob_bioclim)

  bioclim_2017 <- filter(adult_2017$data, year >= 2017) %>% filter(year <= 2018) %>%
    mutate(bioclim_2017 = est_non_rf + omega_s)
  bioclim_2017 <- left_join(bioclim_2017, bioclim_2017_multi)

  adult_predictions <- adult_predictions_obj$data
  adult_bioclim <- dplyr::bind_rows(past_predictions, bioclim_2015, bioclim_2017) %>% 
    select(X, Y, year, past_est, blob_bioclim, bioclim_2013, bioclim_2015, bioclim_2017)

  adult_predictions <- left_join(adult_predictions, adult_bioclim)

  saveRDS(adult_predictions, file = paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-mat-2015-cutoff.rds"))

  #################
  #### Immature 
  #################

  imm_biomass <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed", covs, "--", ssid_string, "-prior-", priors, ".rds"
  ))

    nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(imm_biomass$data$year))%>% 
    mutate(do_mlpl_scaled = (log_do - imm_biomass$data$do_mlpl_mean[1]) /(imm_biomass$data$do_mlpl_sd[1]*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)

@@

  nd_pre_2013 <- nd %>% filter(year < 2013)
  im_model_2013 <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed-past-2013-", ssid_string, "-prior-", priors, ".rds"))
  imm_pre_2013 <- predict(im_model_2013, newdata = nd_pre_2013, return_tmb_object = TRUE)

  fake_2013 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) %>% filter(year < 2013 )
  sort(unique(fake_2013$year))
  sort(unique(nd_pre_2013$year))
  imm_2013 <- predict(im_model_2013, newdata = fake_2013, return_tmb_object = TRUE)
  imm_2013$data$year <- imm_2013$data$year + 2

  nd_pre_2015 <- nd %>% filter(year < 2015)
  im_model_2015 <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed-past-2015-", ssid_string, "-prior-", priors, ".rds"))
  imm_pre_2015 <- predict(im_model_2015, newdata = nd_pre_2015, return_tmb_object = TRUE)

  fake_2015 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) %>% filter(year < 2015)
  sort(unique(nd_pre_2015$year))
  sort(unique(fake_2015$year))
  imm_2015 <- predict(im_model_2015, newdata = fake_2015, return_tmb_object = TRUE)
  imm_2015$data$year <- imm_2015$data$year + 2

  nd_pre_2017 <- nd %>% filter(year < 2017)
  im_model_2017 <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed-past-2017-", ssid_string, "-prior-", priors, ".rds"))
  imm_pre_2017 <- predict(im_model_2017, newdata = nd_pre_2017, return_tmb_object = TRUE)

  fake_2017 <- nd %>% 
    mutate(year = year - 2) %>% 
    filter(year > 2007) #%>% filter(year < 2013 )
  sort(unique(fake_2017$year))
  sort(unique(nd_pre_2017$year))

  imm_2017 <- predict(im_model_2017, newdata = fake_2017, return_tmb_object = TRUE)
  imm_2017$data$year <- imm_2017$data$year + 2

  fake_2017_minus4 <- nd %>% 
    mutate(year = year - 4) %>% 
    filter(year > 2007)
  sort(unique(fake_2017_minus4$year))
  imm_2017_multi <- predict(im_model_past, newdata = fake_2017_minus4, return_tmb_object = TRUE)
  imm_2017_multi$data$year <- imm_2017_multi$data$year + 4
  sort(unique(imm_2017_multi$data$year))

 past_predictions <- imm_pre_2015$data %>% 
   mutate(past_est = est, blob_bioclim = est) %>% 
   select(X, Y, year, past_est, blob_bioclim)

  bioclim_2013_start <- filter(imm_pre_2013$data, year >= 2011) %>% filter(year <= 2012) %>%
    mutate(bioclim_2013 = est)
  bioclim_2013_end <- filter(imm_2013$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2013 = est_non_rf + omega_s)
  bioclim_2013 <- dplyr::bind_rows(bioclim_2013_start, bioclim_2013_end)

  bioclim_2015_start <- filter(imm_past$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2015 = est) %>% select(X,Y, year, bioclim_2015)
  bioclim_2013 <- left_join(bioclim_2013, bioclim_2015_start) %>% 
    select(X,Y, year, bioclim_2013, bioclim_2015)
  past_predictions <- left_join(past_predictions, bioclim_2013)

  bioclim_2015 <- filter(imm_2015$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(blob_bioclim = est_non_rf + omega_s, bioclim_2015 = est_non_rf + omega_s) 
  bioclim_2017_start <- filter(imm_2017$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(bioclim_2017 = est) %>% select(X,Y, year, bioclim_2017)

  bioclim_2015 <- left_join(bioclim_2015, bioclim_2017_start)

  bioclim_2017_multi <- filter(imm_2017_multi$data, year >= 2017) %>% filter(year <= 2018) %>%
    mutate(blob_bioclim = est_non_rf + omega_s) %>% 
    select(X,Y, year, blob_bioclim)

  bioclim_2017 <- filter(imm_2017$data, year >= 2017) %>% filter(year <= 2018) %>%
    mutate(bioclim_2017 = est_non_rf + omega_s)
  bioclim_2017 <- left_join(bioclim_2017, bioclim_2017_multi)

   imm_predictions <- imm_predictions_obj$data
   imm_bioclim <- dplyr::bind_rows(past_predictions, bioclim_2015, bioclim_2017) %>% 
    select(X, Y, year, past_est, blob_bioclim, bioclim_2013, bioclim_2015, bioclim_2017)

  imm_predictions <- left_join(imm_predictions, imm_bioclim)

  saveRDS(imm_predictions, file = paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-imm-2015-cutoff.rds"))

} else { # need to add non-split-by-age version
    # total_biomass <- readRDS(paste0("data/", spp, 
    #   "/model-total-biomass-", spp, "-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))
    # 
    # nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
    # nd <- nd_all %>% 
    #   filter(ssid %in% model_ssid) %>%
    #   filter(year %in% unique(total_biomass$data$year))%>% 
    # mutate(do_mlpl_scaled = (log_do - total_biomass$data$do_mlpl_mean) /(total_biomass$data$do_mlpl_sd*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
    # nd <- na.omit(nd)
    # nd$year <- as.integer(nd$year)
    # 
    # predictions <- predict(total_biomass, newdata = nd)
    # saveRDS(predictions, file = paste0("data/", spp,
    #   "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"))
}
```

@@

if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS( paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-mat-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid))
  try(imm_predictions <- readRDS(paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-imm-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid))

@@

 try({adult_predictions <- readRDS( paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-mat-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid)})
 try({imm_predictions <- readRDS(paste0("data/", spp,
    "/bioclimatic-predictions-", spp, covs,"-", ssid_string, "-imm-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid)})

@@

@@

if (exists("adult_predictions")) {
  # to convert from kg/m2 to kg/hectare multiply by 10000
  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000
  adult_predictions$total_bio <- imm_predictions$est_exp + adult_predictions$est_exp

  # check that both dataframes are arranged similarly
  if (adult_predictions[30000,6] == imm_predictions[30000,6]) {
  imm_predictions$prop_imm <- 
  imm_predictions$est_exp / (adult_predictions$est_exp + imm_predictions$est_exp)
  }

@@

  predictions$est_exp <- exp(predictions$est) * 10000

  # predictions <- predictions %>% group_by(X,Y) %>% arrange(year) %>% mutate(lag_epsilon = lag(epsilon_st), bioclimatic = est - epsilon_st + lag_epsilon)
  # 
  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .999)
  #max_bio <- round(max(predictions$total_bio))
  max_bio <- signif(max(predictions$est_exp), digits = 2)

@@

Save trend plots
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/trends-", spp, covs, "-", ssid_string, "-fixed-everything-noAR1.png"),
  res = 600,
  units = "in",
  width = 11,
  height = 8.5
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

@@

png(
  file = paste0("figs/", spp, "/bioclimatic-biomass-", spp, covs, "-", ssid_string, "-fixed-everything-noAR1.png"),
  res = 600,
  units = "in",
  width = 16,
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = biomass_plots,
  nrow = 2
)
dev.off()
```

Save plot medley
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/bioclimatic-exploratory-", spp, covs, "-", ssid_string, "-fixed-everything-noAR1.png"),
  res = 600,
  units = "in",
  width = 9.5,
  height = 12.5
)

@@

png(
  file = paste0("figs/", spp, "/bioclimatic-residuals-", spp, covs, "-", ssid_string, "-fixed-everything-noAR1.png"),
  res = 600,
  units = "in",
  width = 16,
  height = 8.5
)
gridExtra::grid.arrange(
  grobs = p_adult_st,
  nrow = 2
)
dev.off()
```
